### 2017-04-07 paper/evaluation.tex
done rq5

Considering question 2, participants responded that
\emailsSequential{} of the \emailsProjectsAnswered{} projects did not
execute tests in parallel.  This mismatch is justified by cases where
neither of our checks (static or dynamic) could detect presence of
parallelism.

We investigated this six projects further, and one of them contained a
false-negative result from \numRQC{}, which means that a \pomf{}
is compacted inside a \CodeIn{jar} file. One of them considered a
distributed CI server as parallelism. Two of those projects had a
custom JUnit test runner, which handles the parallelism itself. The
last two projects run the parallelism inside the test method, one runs
a manually created Thread to run some tests, and the other runs in
parallel by using Java 8 collection streams, that allows the
developers to iterate over a list in parallel.

>>>>

Considering question 2, the answers we collected show that six of the
\emailsProjectsAnswered{} projects execute tests in parallel.  This
mismatch is justified by cases where neither of our checks (static or
dynamic) could detect presence of parallelism.  A closer look at these
projects revealed that one of them contained a \emph{pom.xml} file
encapsulated in a jar file (similar case as reported in
Section~\ref{sec:rqC-2}), in one of the projects the particpant
considered that distributed CI was a form of parallelism, and in four
projects parallelism was implemented natively~---~two projects
implemented concurrency control with custom JUnit test runners and two
other projects implemented concurrency within test methods.  Note
that, considering four extra cases (ignored two distributed CI cases),
the usage of parallelization increases from \percentParallel{} to
\percentParallelUpdated{}.  However, we do not consider this change
significant enough to modify our conclusion about practical adoption
of parallelization (\numRQC{}).

%% , one runs a manually created Thread to run some
%% tests, and the other runs in parallel by using Java 8 collection
%% streams, that allows the developers to iterate over a list in
%% parallel.
